\section{Outlines}
\subsection{Job's Bothersome Questions (Part I)}
\textbf{Introduction:} Job 3:20 starts a series of troubling questions from Job. These are beyond the commonly known ``why do the righteous suffer?'':%\footnote{2 June 2016, Keith Anthony}
\index[speaker]{Keith Anthony!Job 03 (Job's Bothersome Questions (Part I))}
\index[series]{Job (Keith Anthony)!Job 03 (Job's Bothersome Questions (Part I))}
\index[date]{2016/06/02!Job 03 (Job's Bothersome Questions (Part I)) (Keith Anthony)}
\begin{compactenum}[I.][19]
    \item  \textbf{Wherefore is light given to him that is
in misery, and life unto the bitter in soul} \index[scripture]{Job!Job 03:20}(Job 3:20)
    \item  \textbf{Why is light given to a man whose way is hid $\hdots$ ?} \index[scripture]{Job!Job 03:23}(Job 3:23)
    \item  \textbf{Shall mortal man be more just than God?} \index[scripture]{Job!Job 04:17}(Job 4:17)
    \item  \textbf{Shall a man be more pure than his maker?} \index[scripture]{Job!Job 04:17}(Job 4:17) 
    \item  \textbf{What is man that thou shouldest magnify him?} \index[scripture]{Job!Job 07:17}(Job 7:17)
    \item  \textbf{If I be wicked, why then labour I in vain?} \index[scripture]{Job!Job 09:29}(Job 9:29)
\end{compactenum}

\subsection{Job's Bothersome Questions (Part II)}
\textbf{Introduction:} Job 3:20 starts a series of troubling questions from Job. These are beyond the commonly known ``why do the righteous suffer?'' (part II):%\footnote{2 June 2016, Keith Anthony}
\index[speaker]{Keith Anthony!Job 03 (Job's Bothersome Questions (Part II))}
\index[series]{Job (Keith Anthony)!Job 03 (Job's Bothersome Questions (Part II))}
\index[date]{2016/06/02!Job 03 (Job's Bothersome Questions (Part II)) (Keith Anthony)}
\begin{compactenum}[I.][19]
    \item  \textbf{Canst thou by searching find out God?} \index[scripture]{Job!Job 11:07}(Job 11:7)
    \item  \textbf{Canst thou find out the Almighty unto perfection?} \index[scripture]{Job!Job 11:07}(Job 11:7)
    \item  \textbf{Man dieth, and wasteth away $\hdots$ and where is he?} \index[scripture]{Job!Job 14:10}(Job 14:10)
    \item  \textbf{What is man that he should be clean?} \index[scripture]{Job!Job 15:14}(Job 15:14)
    \item  \textbf{And he which is born of woman, that he should be righteous?} \index[scripture]{Job!Job 15:14}(Job 15:14)
    \item  \textbf{Wherefore do the wicked live...yea, are mighty in power?} \index[scripture]{Job!Job 21:7}(Job 21:7)
    \item  \textbf{Wherefore do the wicked live...yea, are mighty in power?} \index[scripture]{Job!Job 21:7}(Job 21:7)
\end{compactenum}

\subsection{Job's Bothersome Questions (Part III)}
\textbf{Introduction:} Job 3:20 starts a series of troubling questions from Job. These are beyond the commonly known ``why do the righteous suffer?'' (part 3):%\footnote{2 June 2016, Keith Anthony}
\index[speaker]{Keith Anthony!Job 03 (Job's Bothersome Questions (Part III)}
\index[series]{Job (Keith Anthony)!Job 03 (Job's Bothersome Questions (Part III)}
\index[date]{2016/06/02!Job 03 (Job's Bothersome Questions (Part III)) (Keith Anthony)}
\begin{compactenum}[I.][7]
    \item  \textbf{Can a man be profitable unto God...?} \index[scripture]{Job!Job 22:02}(Job 22:2)
    \item  \textbf{How then can man be justified with God?} \index[scripture]{Job!Job 25:04}(Job 25:4)
    \item  \textbf{Whence then cometh wisdom? Where is $\hdots$understanding?} \index[scripture]{Job!Job 28:20}(Job 28:20)
    \item  \textbf{What profit shall I have if I be cleansed from my sin?} \index[scripture]{Job!Job 35:3}(Job 35:3)
    \item  \textbf{Where is God my maker $\hdots$?} \index[scripture]{Job!Job 35:10}(Job 35:10)
    \item  \textbf{Wilt thou condemn me, that thou mayest be righteous?} \index[scripture]{Job!Job 40:8}(Job 40:8)
    \item  \textbf{Who is he that hideth counsel without knowledge?} \index[scripture]{Job!Job 42:3}(Job 42:3)
\end{compactenum}
\section{Outlines from Others}


\newpage