\subsection{Outlines from Others}

\subsubsection{The Invisible War}
\index[speaker]{sermonnotebook.org!Job 01 (The Invisible War)}
\index[series]{Job (sermonnotebook.org)!Job 01 (The Invisible War)}
\index[date]{2016/01/20!Job 01 (The Invisible War) (sermonnotebook.org)}
%\textbf{Lineage}: adpated from S. Conway\\
\textbf{Introduction}: Everyone in this room knows the reality of hardship and crisis. We have all seen, and most have experienced, some of the obvious tragedies that stalk those who live in this world. There is conflict all around us that we can plainly see. Death, disease, warfare, hardships, pain, sorrow, etc., are all obvious and clearly seen by everyone who lives in this world.  There is an area of conflict that goes on around us and within us that we cannot see. I am referring to the conflict that happens in the spiritual realm. We are all engaged in spiritual warfare, even if we do not realize it. In this war, this war that cannot be seen, there are many casualties. In this war, there are no conscientious objectors. There are only those who are ground up and broken down by the spiritual crises they face in life.   In this text, the veil is pulled back just a little. We are allowed to catch a glimpse of the spiritual warfare that occurred in Job's life. We are allowed to see and understand a little of what transpired behind the scenes in the greatest tragedy of Job's life.   In this text, we are allowed to see events that occurred in Heaven. What a difference it would have made in Job's life had he known what was happening. But, he didn’t; and neither do we.  When trials come our way, we always seem to forget that God is behind our hurts and that He has a plan in our pain. This passage reminds us of that great truth!  I want to take another look at Job's great time of suffering. I want to help us to learn from the warfare that Job faced. There is help here for us when we face our own times of suffering and sorrow. There is help here for those times when our enemies are arrayed against us. There is help here, if we will hear it, and if we will receive it!  I want to preach for a few minutes about The Invisible War. I want to share a few thoughts that present themselves in this passage today. As I preach these things today, please remember that just like Job, we are engaged in battle with a spiritual enemy who seeks our destruction; but like Job, we have One with us Who is able to strengthen us, keep us and see us through any battle we may find ourselves engaged it. Let's investigate The Invisible War.
\begin{compactenum}[I.][4]
	\item An \textbf{Unlikely Candidate} \index[scripture]{Job!Job 01:01-05}(Job 1:1-5) %\footnote{\href{https://www.sermonnotebook.org/old%20testament/Job%201_1-12.htm}{sermonnotebook.org}}
	\item An \textbf{Unseen Conflict} \index[scripture]{Job!Job 01:06-12}(Job 1:6-12)
	\item An \textbf{Unbelievable Crisis} \index[scripture]{Job!Job 01:13-19}(Job 1:13-19)
	\item An \textbf{Unrelinquished Control} \index[scripture]{Job!Job 01:06-12}(Job 1:6-12)
	\item An \textbf{Unfazed Commitment} \index[scripture]{Job!Job 01:20-22}(Job 1:20-22)
\end{compactenum}


