\section{Job 34  Comments}

\subsection{Numeric Nuggets}
\textbf{13:} Verse 12 has 13 words.  Verses 5, 8, and 34 have 13 unique words. The 13-letter words ``transgression'' and ``understanding'' are used in the chapter.


\subsection{Job 34:7-9}
Words are like food. The  Word is likened to:\cite{thomas_20220309}
\begin{compactenum}
    \item Apples
    \item Bread
    \item Milk
    \item Meat
    \item Honey
\end{compactenum}
The point is that for a balanced diet, one needs all of these! If all you get is milk, you cannot and will not grow. See 2 Timothy 2:15.\footnote{\textbf{2 Timothy 2:15} -  Study to shew thyself approved unto God, a workman that needeth not to be ashamed, rightly dividing the word of truth.} In Job 23:12, Job continues the description.\footnote{\textbf{Job 23:12} - Neither have I gone back from the commandment of his lips; I have esteemed the words of his mouth more than my necessary food.} Ezekiel eats the roll in Ezekiel 3:1-3.\footnote{\textbf{Ezekiel 3:1-3} - Moreover he said unto me, Son of man, eat that thou findest; eat this roll, and go speak unto the house of Israel. [2] So I opened my mouth, and he caused me to eat that roll. [3] And he said unto me, Son of man, cause thy belly to eat, and fill thy bowels with this roll that I give thee. Then did I eat it; and it was in my mouth as honey for sweetness.} John continues the description in Revelation 10:10.\footnote{\textbf{Revelation 10:10} - And I took the little book out of the angel’s hand, and ate it up; and it was in my mouth sweet as honey: and as soon as I had eaten it, my belly was bitter.}\cite{thomas_20220309}

\subsection{Job 34:7-9}
Elihu apears to be on the same trail as the other three (see verses 11, 21, 22, 25, and 26). Allusion is to Psalm 1:1 (which had not yer been written.)\footnote{\textbf{Psalm 1:1} - Blessed is the man that walketh not in the counsel of the ungodly, nor standeth in the way of sinners, nor sitteth in the seat of the scornful.} Had Job actually said this? Closest statement might be in Job 21:15 (which really does not say it, but will be misquoted by Elihu).\footnote{\textbf{Jobn 21:15} - What is the Almighty, that we should serve him? and what profit should we have, if we pray unto him?}\\
\\
\noindent Sam Kinison died in the desert, talking to God. The high-decibel comic and former Pentecostal preacher was driving U.S. Highway 95 to a sold-out run in Laughlin, Nev., on the evening of April 10, 1992, when his Trans-Am collided head-on with a pickup truck. After the impact, as the other driver, a 17-year-old boy, reportedly exclaimed, ”Look at my truck!” Kinison stumbled from his car and collapsed, asking God why he had to die, why now. ”Okay,” he finally whispered. ”Okay … okay.”  The calm acceptance was literally a far cry from the howl of outrage Kinison, 38, had made his onstage trademark. His fury thrust itself up out of his past as the outcast, twice-divorced son of two evangelical preachers in Peoria, Ill., driving him from the ministry he had served for six years onto the stage to rant about women, the homeless, and, yes, televangelists. ``The ministry’s a hard thing to live up to,'' he would later say. ``It was probably why I got into the vulgarity so much, because it was just such a trip to be able to live it out.'' Sam Kinnson's final words: Comedian Sam Kinison who died in a head-on collision in 1992 said to no one in particular: ``I don’t want to die. I don’t want to die.'' But then there was a pause as if Kinison were listening to someone. Then he asked, “But why?” and after another pause ``Okay, Okay, Okay.'' A friend who was with him said, ``Whatever voice was talking to him gave him the right answer and he just relaxed with it.''\cite{thomas_20220309}

\subsection{Job 34:10-12}
See Genesis 18:25 concerning the destruction of Sodom, but saving Lot and his family.\footnote{\textbf{Genesis 18:25} - That be far from thee to do after this manner, to slay the righteous with the wicked: and that the righteous should be as the wicked, that be far from thee: Shall not the Judge of all the earth do right?}.\cite{thomas_20220309}

\subsection{Job 34:13-14}
You are not telling God what to do! God will certainly not let you! See Proverb 19:21 concerning the counsel of the Lord.\footnote{\textbf{Proverb 19:21} - There are many devices in a man’s heart; nevertheless the counsel of the LORD, that shall stand.}\cite{thomas_20220309}

\subsection{Job 34:14}
God's breath is the source of all animal life. Ses Genesis 2:7 and Ecclesiastes 3:20-21.\footnote{\textbf{Genesis 2:7} - And the LORD God formed man of the dust of the ground, and breathed into his nostrils the breath of life; and man became a living soul.}\footnote{\textbf{Ecclesiastes 3:20-21} - All go unto one place; all are of the dust, and all turn to dust again. [21] Who knoweth the spirit of man that goeth upward, and the spirit of the beast that goeth downward to the earth?} See Psalm 104:29-30.\footnote{\textbf{Psal 104:29-20} - Thou hidest thy face, they are troubled: thou takest away their breath, they die, and return to their dust. [30] Thou sendest forth thy spirit, they are created: and thou renewest the face of the earth.} God gathers his breath in Genesis 6:7.\footnote{\textbf{Genesis 6:7} - And the LORD said, I will destroy man whom I have created from the face of the earth; both man, and beast, and the creeping thing, and the fowls of the air; for it repenteth me that I have made them.}

\subsection{Job 34:14-15}
Only the flesh and spirit are spoken of, supporting the truth that for un-redeemed sinners the soul and spirit are joined.\cite{thomas_20220309}