\section{Job 3  Comments}

\subsection{Numeric Nuggets}
There are 13 words in Job 3:14, 17, and 18. In these verses, respectively, ``kings and counselors,'' ''the wicked,'' and ``prisoners,'' appear.

\subsection{Job 3:5}
What is this ``shadow of death?'' Job 3:5 is the first mention of the phrase, found 20 times in scripture, listed in Table ~\ref{table:The ``shadow of death'' in scripture}. Ruckman identified this mysterious thing as ``the cloud of death will move across this earth in the Tribulation, distributing death-dealing radioactivity to anything underneath it.''\cite{ruckman1993Job}

%%%%%%%%%%
%%%%%%%%%%

\normalsize
 
\begin{center}
\begin{longtable}{p{1in}|p{3.50in}}
\caption[The ``shadow of death'' in scripture]{The ``shadow of death'' in scripture}\label{table:The ``shadow of death'' in scripture} \\
\hline \multicolumn{1}{|c|}{\textbf{Reference}} & \multicolumn{1}{c|}{\textbf{Verse}} \\ \hline 
\endfirsthead
 
\multicolumn{2}{c}
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\  
\hline \multicolumn{1}{|c|}{\textbf{Reference}} & \multicolumn{1}{c|}{\textbf{Verse}} \\ \hline 
\endhead
 
\hline \multicolumn{2}{c}{{ }} \\ \hline
\endfoot 
Job 3:5 & Let darkness and the shadow of death stain it; let a cloud dwell upon it; let the blackness of the day terrify it. \\ \hline 
Job 10:21  & Before I go whence I shall not return, even to the land of darkness and the shadow of death;\\ \hline
Job 10:22  & A land of darkness, as darkness itself; and of the shadow of death, without any order, and where the light is as darkness.\\ \hline
Job 12:22  & He discovereth deep things out of darkness, and bringeth out to light the shadow of death.\\ \hline
Job 16:16  & My face is foul with weeping, and on my eyelids is the shadow of death;\\ \hline
Job 24:27 & For the morning is to them even as the shadow of death: if one know them, they are in the terrors of the shadow of death.\\ \hline
Job 28:3 & He setteth an end to darkness, and searcheth out all perfection: the stones of darkness, and the shadow of death. \\ \hline
Job 34:22 & There is no darkness, nor shadow of death, where the workers of iniquity may hide themselves. \\ \hline
Job 38:17 & Have the gates of death been opened unto thee? or hast thou seen the doors of the shadow of death?\\ \hline
Psalm 23:4 & Yea, though I walk through the valley of the shadow of death, I will fear no evil: for thou art with me; thy rod and thy staff they comfort me. \\ \hline
Psalm 44:19 & Though thou hast sore broken us in the place of dragons, and covered us with the shadow of death. \\ \hline
Psalm 107:10 & Such as sit in darkness and in the shadow of death, being bound in affliction and iron;\\ \hline
Psalm 107:14 & He brought them out of darkness and the shadow of death, and brake their bands in sunder.\\ \hline
Isaiah 9:2 & The people that walked in darkness have seen a great light: they that dwell in the land of the shadow of death, upon them hath the light shined. \\ \hline
Jeremiah 2:6 & Neither said they, Where is the LORD that brought us up out of the land of Egypt, that led us through the wilderness, through a land of deserts and of pits, through a land of drought, and of the shadow of death, through a land that no man passed through, and where no man dwelt? \\ \hline
Jeremiah 13:16 & Give glory to the LORD your God, before he cause darkness, and before your feet stumble upon the dark mountains, and, while ye look for light, he turn it into the shadow of death, and make it gross darkness. \\ \hline
Amos 5:8 & Seek him that maketh the seven stars and Orion, and turneth the shadow of death into the morning, and maketh the day dark with night: that calleth for the waters of the sea, and poureth them out upon the face of the earth: The LORD is his name: \\ \hline
Matthew 4:16 & The people which sat in darkness saw great light; and to them which sat in the region and shadow of death light is sprung up.\\ \hline
Luke 1:79 & To give light to them that sit in darkness and in the shadow of death, to guide our feet into the way of peace. \\ \hline
\end{longtable}
\end{center}



%%%%%%%%%%
%%%%%%%%%%


\subsection{Job 3:16}
One of the types evident in Job is Paul as a type of Tribulation Saints (``one born out of due time,'' in 1 Corinthians 15:8).

